Illusion Game Validation (Study 2)

### 2022-08-06 study1/study1.Rmd
update stim

# This is a local folder containing raw data from unzipped pavlovia
# It has been added to .gitignore to NOT be published on github
# (it contains the subject ID of the participants)
participants <- list.files("study1/data/")

df <- data.frame()
for (ppt in participants) {
  df <- rbind(df, preprocess_raw(file = paste0("study1/rawdata/", ppt)))
}

@@

# Save anonymized data
write.csv(df, "data/study1.csv", row.names = FALSE)
```

@@

df <- read.csv("data/study1.csv") |>
  mutate(
    Date = as.Date(Date),
    Participant = fct_reorder(Participant, Date),
    Screen_Refresh = as.character(Screen_Refresh),
    Illusion_Side = as.factor(Illusion_Side),
    Block = as.factor(Block),
    Education = fct_relevel(Education, "Master", "Bachelor", "High School", "Other")
  )
```

>>>>

# This is a local folder containing raw data from unzipped pavlovia
# It has been added to .gitignore to NOT be published on github
# (it contains the subject ID of the participants)
participants <- list.files("data/")

df <- data.frame()
for (ppt in participants) {
  df <- rbind(df, preprocess_raw(file = paste0("data/", ppt)))
}

@@

# Save anonymized data
write.csv(df, "../data/study1.csv", row.names = FALSE)
```

@@

df <- read.csv("../data/study1.csv") |>
  mutate(
    Date = as.Date(Date),
    Participant = fct_reorder(Participant, Date),
    Screen_Refresh = as.character(Screen_Refresh),
    Illusion_Side = as.factor(Illusion_Side),
    Block = as.factor(Block),
    Education = fct_relevel(Education, "Master", "Bachelor", "High School", "Other")
  )
```

### 2022-08-06 study2/study2.Rmd
update stim

# This is a local folder containing raw data from unzipped pavlovia
# It has been added to .gitignore to NOT be published on github
# (it contains the subject ID of the participants)
participants <- list.files("study2/data/")

df <- data.frame()
for (ppt in participants) {
  df <- rbind(df, preprocess_raw(file = paste0("study2/data/", ppt)))
}

@@

# Save anonymized data
write.csv(df, "data/study2.csv", row.names = FALSE)
```

@@

df <- read.csv("data/study2.csv") |>
  mutate(
    Date = as.Date(Date),
    Participant = fct_reorder(Participant, Date),
    Screen_Refresh = as.character(Screen_Refresh),
    Illusion_Side = as.factor(Illusion_Side),
    Block = as.factor(Block)
    # Education = fct_relevel(Education, "Master", "Bachelor", "High School", "Other")
  )
```

@@

### Model Visualization

@@

  # Assign color from the same palette to every observation of data (for geom_dots)
  closest <- diffvals[max.col(-abs(outer(data[[vars[1]]], diffvals, "-")))]
  data$color <- colors[as.character(closest)]
  data$color <- fct_reorder(data$color, closest)

@@

  pred |>
    ggplot(aes_string(x = varstrength, y = "Predicted")) +
    geom_dots(
      data = data,
      aes(x=x, 
          y = Error, 
          group = Error,
          side = .dots_side, 
          # order=as.numeric(color) * ifelse(Error == 1, 1, -1)), 
          order=color), 
      fill = data$color,
      color = NA, 
      alpha=0.5) +
    geom_slab(data=data, aes(y = Error)) +
    geom_ribbon(aes_string(ymin = "CI_low", ymax = "CI_high", fill = vardiff, group = vardiff), alpha = 0.2) +
    geom_vline(xintercept = 0, linetype = "dashed") +
    geom_hline(yintercept = c(0.05, 0.5, 0.95), linetype = "dotted", alpha = 0.5) +
    geom_line(aes_string(color = vardiff, group = vardiff)) +
    scale_y_continuous(limits = c(0, 1), expand = c(0, 0), labels = scales::percent) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_color_gradientn(colours = c("#F44336", "#FFC107", "#4CAF50")) +
    scale_fill_gradientn(colours = c("#F44336", "#FFC107", "#4CAF50")) +
    coord_cartesian(xlim=c(min(data[[varstrength]]), max(data[[varstrength]]))) +
    theme_modern() +
    labs(
      title = paste0(data$Illusion_Type[1], " Illusion"),
      color = "Difficulty", fill = "Difficulty",
      y = "Probability of Error",
      x = "Illusion Strength"
    ) +
    theme(plot.title = element_text(face = "bold", hjust = 0.5))
}

plot_model_err(data, model_delboeuf_err)
```

@@

@@

### Model Visualization

@@

  # Assign color from the same palette to every observation of data (for geom_dots)
  closest <- diffvals[max.col(-abs(outer(data[[vars[1]]], diffvals, "-")))]
  data$color <- colors[as.character(closest)]
  data$color <- fct_reorder(data$color, closest)

  pred |>
    ggplot(aes_string(x = varstrength, y = "Predicted")) +
    geom_dots(
      data = data,
      aes(x=x, 
          y = Error, 
          group = Error,
          side = .dots_side, 
          # order=as.numeric(color) * ifelse(Error == 1, 1, -1)), 
          order=color), 
      fill = data$color,
      color = NA, 
      alpha=0.5) +
    geom_slab(data=data, aes(y = Error)) +
    geom_ribbon(aes_string(ymin = "CI_low", ymax = "CI_high", fill = vardiff, group = vardiff), alpha = 0.2) +
    geom_vline(xintercept = 0, linetype = "dashed") +
    geom_hline(yintercept = c(0.05, 0.5, 0.95), linetype = "dotted", alpha = 0.5) +
    geom_line(aes_string(color = vardiff, group = vardiff)) +
    scale_y_continuous(limits = c(0, 1), expand = c(0, 0), labels = scales::percent) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_color_gradientn(colours = c("#F44336", "#FFC107", "#4CAF50")) +
    scale_fill_gradientn(colours = c("#F44336", "#FFC107", "#4CAF50")) +
    coord_cartesian(xlim=c(min(data[[varstrength]]), max(data[[varstrength]]))) +
    theme_modern() +
    labs(
      title = paste0(data$Illusion_Type[1], " Illusion"),
      color = "Difficulty", fill = "Difficulty",
      y = "Probability of Error",
      x = "Illusion Strength"
    ) +
    theme(plot.title = element_text(face = "bold", hjust = 0.5))
}

plot_model_err(data, model_delboeuf_err)
```

>>>>

# This is a local folder containing raw data from unzipped pavlovia
# It has been added to .gitignore to NOT be published on github
# (it contains the subject ID of the participants)
participants <- list.files("data/")

df <- data.frame()
for (ppt in participants) {
  df <- rbind(df, preprocess_raw(file = paste0("data/", ppt)))
}

@@

# Save anonymized data
write.csv(df, "../data/study2.csv", row.names = FALSE)
```

@@

df <- read.csv("../data/study2.csv") |>
  mutate(
    Date = as.Date(Date),
    Participant = fct_reorder(Participant, Date),
    Screen_Refresh = as.character(Screen_Refresh),
    Illusion_Side = as.factor(Illusion_Side),
    Block = as.factor(Block)
    # Education = fct_relevel(Education, "Master", "Bachelor", "High School", "Other")
  )
```

@@

##### Model Visualization

@@

  # Assign color from the same palette to every observation of data (for geom_dots)
  closest <- diffvals[max.col(-abs(outer(data[[vardiff]], diffvals, "-")))]
  data$color <- colors[as.character(closest)]
  data$color <- fct_reorder(data$color, closest)

@@

  pred |>
    ggplot(aes_string(x = varstrength, y = "Predicted")) +
    geom_dots(
      data = data,
      aes(x=x, 
          y = Error, 
          group = Error,
          side = .dots_side, 
          # order=as.numeric(color) * ifelse(Error == 1, 1, -1)), 
          order=color), 
      fill = data$color,
      color = NA, 
      alpha=0.5) +
    geom_slab(data=data, aes(y = Error)) +
    geom_ribbon(aes_string(ymin = "CI_low", ymax = "CI_high", fill = vardiff, group = vardiff), alpha = 0.2) +
    geom_vline(xintercept = 0, linetype = "dashed") +
    geom_hline(yintercept = c(0.5), linetype = "dotted", alpha = 0.5) +
    geom_line(aes_string(color = vardiff, group = vardiff)) +
    scale_y_continuous(limits = c(0, 1), expand = c(0, 0), labels = scales::percent) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_color_gradientn(colours = c("#F44336", "#FFC107", "#4CAF50")) +
    scale_fill_gradientn(colours = c("#F44336", "#FFC107", "#4CAF50")) +
    coord_cartesian(xlim=c(min(data[[varstrength]]), max(data[[varstrength]]))) +
    theme_modern() +
    labs(
      title = paste0(data$Illusion_Type[1], " Illusion"),
      color = "Difficulty", fill = "Difficulty",
      y = "Probability of Error",
      x = "Illusion Strength"
    ) +
    theme(plot.title = element_text(face = "bold", hjust = 0.5))
}

p_delboeuf_err <- plot_model_err(data, model_delboeuf_err)
p_delboeuf_err
```

@@

```{r message=FALSE, warning=FALSE, cache=cache}
formula <- brms::bf(
  RT ~ Illusion_Difference * Illusion_Strength + 
    (1 + (Illusion_Difference * Illusion_Strength) | Participant),
  family="shifted_lognormal"
)

# prior = c(
#     prior(normal(6, 1.5), class = Intercept),
#     prior(normal(0, 1), class = sigma),
#     prior(normal(0, .01), class = b, coef = c_trial)
#   )

@@

model_delboeuf_rt <- brms::brm(formula,
  data = data,
  refresh = 0
)

modelbased::estimate_prediction(model_delboeuf_rt, keep_iterations = 10) |> 
  as.data.frame() |> 
  head()
  bayestestR::reshape_iterations()
nrow(as.data.frame(pred))
performance::check_model(model_delboeuf_rt)
# parameters::parameters(model)
```

##### Model Visualization

```{r message=FALSE, warning=FALSE, cache=cache}
plot_model_rt <- function(data, model) {
  data <- mutate(data, .dots_side = ifelse(Error == 1, "bottom", "top"))

@@

  # Assign color from the same palette to every observation of data (for geom_dots)
  closest <- diffvals[max.col(-abs(outer(data[[vardiff]], diffvals, "-")))]
  data$color <- colors[as.character(closest)]
  data$color <- fct_reorder(data$color, closest)

  p <- pred |>
    ggplot(aes_string(x = varstrength, y = "Predicted")) +
    ggdist::stat_slab(data=data, aes_string(y="RT", group = vardiff, fill=vardiff), alpha=0.5) +
    geom_ribbon(aes_string(ymin = "CI_low", ymax = "CI_high", fill = vardiff, group = vardiff), alpha = 0.2) +
    geom_vline(xintercept = 0, linetype = "dashed") +
    geom_line(aes_string(color = vardiff, group = vardiff)) +
    scale_y_continuous(expand = c(0, 0)) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_color_gradientn(colours = c("#F44336", "#FFC107", "#4CAF50")) +
    scale_fill_gradientn(colours = c("#F44336", "#FFC107", "#4CAF50")) +
    coord_cartesian(xlim=c(min(data[[varstrength]]), max(data[[varstrength]])),
                    ylim=c(150, 2000)) +
    theme_modern() +
    labs(
      title = paste0(data$Illusion_Type[1], " Illusion"),
      color = "Difficulty", fill = "Difficulty",
      y = "Reaction Time (ms)",
      x = "Illusion Strength"
    ) +
    theme(plot.title = element_text(face = "bold", hjust = 0.5))

}

p_delboeuf_rt <- plot_model_rt(data, model_delboeuf_rt)
p_delboeuf_rt
```

#### Visualization

```{r message=FALSE, warning=FALSE, cache=cache, fig.height=fig.height*2}
plot_all <- function(data, p_err, p_rt) {
  # Get stimuli
  dat <- df |>
    filter(Error == 0) |> 
    filter(Illusion_Type == unique(data$Illusion_Type),
           Answer %in% c("arrowleft", "arrowup")) |>
    select(Stimulus, Illusion_Strength, Illusion_Difference)

  dat <- rbind(
    filter(dat, Illusion_Strength == min(Illusion_Strength)) |> 
    filter(Illusion_Difference %in% c(min(Illusion_Difference), max(Illusion_Difference))),
    filter(dat, Illusion_Strength == max(Illusion_Strength)) |> 
    filter(Illusion_Difference %in% c(min(Illusion_Difference), max(Illusion_Difference))),
    filter(dat, Illusion_Difference == min(Illusion_Difference)) |> 
    filter(Illusion_Strength %in% c(min(Illusion_Strength), max(Illusion_Strength))),
    filter(dat, Illusion_Difference == max(Illusion_Difference)) |> 
    filter(Illusion_Strength %in% c(min(Illusion_Strength), max(Illusion_Strength))))

  img_leftdown <- filter(dat, Illusion_Difference == max(Illusion_Difference)) |> 
    filter(Illusion_Strength == min(Illusion_Strength)) |> 
    pull(Stimulus) |> 
    unique()
  img_rightdown <- filter(dat, Illusion_Difference == max(Illusion_Difference)) |> 
    filter(Illusion_Strength == max(Illusion_Strength)) |> 
    pull(Stimulus) |> 
    unique()
  img_leftup <- filter(dat, Illusion_Strength == min(Illusion_Strength)) |> 
    filter(Illusion_Difference == min(Illusion_Difference)) |> 
    pull(Stimulus) |> 
    unique()
  img_rightup <- filter(dat, Illusion_Strength == max(Illusion_Strength)) |> 
    filter(Illusion_Difference == min(Illusion_Difference)) |> 
    pull(Stimulus) |> 
    unique()

  img_leftdown <- paste0("study2/stimuli/", img_leftdown, ".png") |> 
    png::readPNG() |> 
    grid::rasterGrob(interpolate=TRUE) |> 
    patchwork::wrap_elements()
  img_rightdown <- paste0("study2/stimuli/", img_rightdown, ".png") |> 
    png::readPNG() |> 
    grid::rasterGrob(interpolate=TRUE) |> 
    patchwork::wrap_elements()
  img_leftup <- paste0("study2/stimuli/", img_leftup, ".png") |> 
    png::readPNG() |>  
    grid::rasterGrob(interpolate=TRUE) |> 
    patchwork::wrap_elements()
  img_rightup <- paste0("study2/stimuli/", img_rightup, ".png") |> 
    png::readPNG() |> 
    grid::rasterGrob(interpolate=TRUE) |> 
    patchwork::wrap_elements()

  p <- ((p_err + labs(x = "")) / (p_rt + labs(title = "")) + patchwork::plot_layout(guides="collect"))

  # (
  #   (img_leftup / patchwork::plot_spacer() / img_leftdown + patchwork::plot_layout(heights = c(0.5, 2, 0.5))) | 
  #   (patchwork::plot_spacer() / p / patchwork::plot_spacer()  + patchwork::plot_layout(heights = c(0.5, 2, 0.5))) | 
  #   (img_rightup / patchwork::plot_spacer() / img_rightdown  + patchwork::plot_layout(heights = c(0.5, 2, 0.5)))
  #   ) + 
  #   patchwork::plot_layout(widths = c(0.5, 1, 0.5))

  (img_leftup | patchwork::plot_spacer() | img_rightup) / p / (img_leftdown | patchwork::plot_spacer() | img_rightdown) + 
    patchwork::plot_layout(heights = c(0.5, 1.5, 0.5))
}

p_delboeuf <- plot_all(data, p_delboeuf_err, p_delboeuf_rt)
p_delboeuf
```
